%-------------------------
% Resume in Latex
% Author : Aditya Godse
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

% -------------------- PACKAGE IMPORTS --------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[version=4]{mhchem}

% Unicode support for PDFs (makes it ATS parsable)
\input{glyphtounicode}

% -------------------- PAGE LAYOUT --------------------
\pagestyle{fancy}
\fancyhf{}                          % Clear default header/footer
\fancyfoot{}                        % No footer
\renewcommand{\headrulewidth}{0pt}  % Remove header rule
\renewcommand{\footrulewidth}{0pt}  % Remove footer rule

% Adjusting margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.50in}
\addtolength{\textheight}{1.0in}

% URL formatting
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}  % Control the space between columns in tabularx

% -------------------- SECTION FORMATTING --------------------
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generated PDFs are machine-readable (ATS parsable)
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
% Item list with custom spacing
\newcommand{\customSmallList}[2]{%
  \begin{itemize}[leftmargin=0.15in, label={}, itemsep=#1, parsep=#2]
    \footnotesize
    #2
  \end{itemize}%
}

% Command for single resume item
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Command for adding a resume subheading (institution, date, role)
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

% Command for a sub-subheading within a resume
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% Command for project heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

% Command to start/end subheading list
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% Command to start/end item list
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Changing bullet point style for nested itemize
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Adjusting footer height
\setlength{\footskip}{4.08003pt}

% -----------------------------------------------------------
% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{center}
  \textbf{\Huge \scshape Aditya Godse} \\ \vspace{8pt}
  \small
  \faIcon{github} \href{https://github.com/adimail}{\underline{\textcolor{blue}{github.com/adimail}}} $  $
  \faIcon{globe} \href{https://adimail.github.io/}{\underline{\textcolor{blue}{adimail.github.io}}} $  $
  \faIcon{linkedin} \href{https://www.linkedin.com/in/adimail2404/}{\underline{\textcolor{blue}{linkedin/adimail2404}}} $  $
  \faIcon{envelope} \href{mailto:adimail2404@gmail.com}{\underline{\textcolor{blue}{adimail2404@gmail.com}}}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AISSMS Institute of Information Technology}{June 2026}
      {Bachelor of Technology in Artificial Intelligence and Data Science}{CGPA: 7.72/10, Pune, India}
    \resumeItemListStart
      \resumeItem{Minor Course: Instrumentation Engineering}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item \textbf{Languages}{: Python, C/C++, bash, Perl, Go, Javascript, Typescript}
        \item \textbf{Tools}{: scikit-learn, tensorflow, Pytorch, OpenCV, GitHub Actions, CI/CD pipelines, Shell scripts, Docker, Next.JS}
    }
\end{itemize}

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Webmaster, \href{https://ioit.acm.org/}{IOIT ACM Student Chapter}} $|$ \footnotesize\emph{Management, SEO, DevOps}}{Sept. 2024 - Present}
    \resumeItemListStart
        \resumeItem{Designed and developed the \href{https://ioittenet.com/}{\textbf{IOIT TENET}} website, reaching 15,000 users within just 3 weeks.}
        \resumeItem{Increased event registration by implementing custom forms and building visually engaging 3D animations using GSAP, Three.js, and WebGL.}
        \resumeItem{\href{https://www.ioittenet.com/events/web3-panel}{Moderated a \textbf{Web3 panel discussion} at TENET'24 before an audience of 200 students.}}
    \resumeItemListEnd

    % \resumeProjectHeading
    % {\textbf{Chief Technology Officer, Hosteze (Startup)} $|$ \footnotesize\emph{AWS, System Design, GraphQL, Next.JS}}{Feb. 2024 - Sept 2024}
    % \resumeItemListStart
    %     \resumeItem{Led the design, development, testing, and maintenance of the core product, ensuring seamless functionality while maintaining comprehensive technical documentation for the entire codebase.}
    %     \resumeItem{Built an internal CRM tool with an ETL data pipeline that analyzes over 500 housing listings weekly to improve customer outreach.}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd

% -------------------- OPEN SOURCE --------------------
\section{Open Source}
  \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{\href{https://github.com/openssl/openssl/pull/25796}{OpenSSL}} $|$ \footnotesize\emph{C, Perl, testing, bash}}{Oct. 2024 - Present}
    \resumeItemListStart
        \resumeItem{\href{https://github.com/openssl/openssl/pull/25796}{Implemented new -cipher CLI option in OpenSSL's req command enabling users to specify private key encryption algorithms, enhancing security flexibility beyond previous default 3DES encryption. (PR:25796)}}
        \resumeItem{Updated default ciphers for for req, cms and smime apps, and updated documentation for man pages and usage examples, following OpenSSL's strict coding and documentation standards. (PR: 25839)}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


% -------------------- PROJECTS --------------------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\href{https://github.com/adimail/fantasy-sports-machine-learning}{\textbf{Fantasy Sports optimisation algorithm}} $|$ \footnotesize\emph{Linear programming, XGBoost, PuLP, MLOps, Docker}}{Feb. 2025}
    \resumeItemListStart
        \resumeItem{Engineered an \textbf{AI-driven optimization model} using XGBoost and linear programming (PuLP) to automate fantasy team selection, leveraging extensive research on player stats and game dynamics.}
        \resumeItem{Pioneered a \textbf{multi-constraint algorithm} balancing budget, player roles, and recent form, achieving 32\% higher accuracy than traditional rule-based systems.}
        \resumeItem{Spearheaded end-to-end development: \textbf{web scraping ESPN data}, preprocessing with Pandas, and deploying MLOps pipelines for scalable retraining.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\href{https://github.com/adimail/torrent-client}{\textbf{Fun with flags (Multiplayer Game)}} $|$ \footnotesize\emph{Go, WebSockets}}{Jan. 2025}
    \resumeItemListStart
        \resumeItem{Designed and developed a web-based multiplayer game with interactive challanges.}
        \resumeItem{Engineered a full-duplex WebSocket service with Golang for realtime game communication supporting up to 10 concurrent players in multiplayer mode and 10 rooms}
    \resumeItemListEnd


    \resumeProjectHeading
    {\href{https://mermaid-mind.vercel.app/}{\textbf{Mermaid Mind (Web/LLM)}} $|$ \footnotesize\emph{Monaco Editor, LLM, Gemini, Next.js, MongoDB, NextAuth, tRPC}}{May. 2024}
    \resumeItemListStart
        \resumeItem{Built a web application that converts natural language inputs into Mermaid diagrams using LLMs. Fine-tuned \textbf{Deepseek R1} on a custom dataset to improve diagram generation accuracy, achieving significantly better results compared to the base model. For production, I used the \textbf{Gemini 1.5 Pro} model.}

        \resumeItem{Designed and implemented the LLM pipeline to process natural language inputs, extract key entities, and generate valid Mermaid syntax. I followed good prompt engineering techniques to ensure high-quality outputs and reduce errors in diagram generation.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\href{https://github.com/adimail/moneyball-native}{\textbf{Moneyball (Android/IOS/Web)}} $|$ \footnotesize\emph{React Native, JavaScript, Firebase, Google Cloud, Mobile Development}}{Feb. 2024}
    \resumeItemListStart
        \resumeItem{Cross-platform application to manage financial history with Firebase as a backend.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\href{https://github.com/adimail/torrent-client}{\textbf{bittorrent client (CLI Tool)}} $|$ \footnotesize\emph{Go, Concurrency patterns, Bittorrent, Unit Testing, Bencoding}}{Jan. 2024}
    \resumeItemListStart
        \resumeItem{Created a lightweight software application to download large files using the BitTorrent protocol.}
        \resumeItem{A peer-to-peer (P2P) communication protocol for distributing large amounts of data over the internet.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% -------------------- OTHER ACHIEVEMENTS --------------------
\section{Other Achievements}
\begin{itemize}
    \footnotesize
    \setlength\itemsep{-1pt}
    \item Title Holder for Asia's Largest Painting on Recycled Paper Canvas \hfill (Aug. 2021)
    \item Scientist of the Year Award in highschool for Active Participation in Science Fairs \hfill (Feb. 2019)
    \item 2-time National Level Rope Skipping Gold Medalist (Double unders \& Spot jump) \hfill (2016 - 2017)
\end{itemize}

\end{document}
